### 2020-11-10 docs/manuscript.tex
update abstract

\usepackage{parskip}
\usepackage{microtype}
\usepackage{svg}
\usepackage{float}
\usepackage{placeins}
\usepackage[english]{babel} % Specify a different language here - english by default
\usepackage{listings}
\usepackage{fontspec}
\usepackage{transparent}
% \usepackage{lipsum} % Required to insert dummy text. To be removed otherwise
\setmainfont{TeX Gyre Termes}
%----------------------------------------------------------------------------------------
%	COLUMNS
%----------------------------------------------------------------------------------------

@@

\Authors{Daniel Habermann\textsuperscript{1}, Daniel Hoffmann\textsuperscript{1}} % Authors
\affiliation{\textsuperscript{1}\textit{Department of Biology, University of Duisburg-Essen, Essen, Germany}} % Author affiliation
% \affiliation{\textsuperscript{2}\textit{Department of Chemistry, University of Examples, London, United Kingdom}} % Author affiliation
% \affiliation{*\textbf{Corresponding author}: john@smith.com} % Corresponding author

@@

\Abstract{
  % - what are HLA associated mutations and why identifying HLA escape is important
  % 
  % - current methods lack important aspects
  % - Progress in Bayesian methods are not reflected in current HLA models
  % - Bayesian statistics provides a coherent framework to combine information from different sources
  % - Using this kind of imformation and new methods improve predicted performance tremendously
  % -
  \\
  \textbf{Motivation} \\
  The human leucoyte antigen system (HLA) is of paramount importance to combat viral
  infections by presenting peptides on the cell surface via MHC I.
  In this way, CD8+ cytotoxic T-Lymphocytes exert a strong selection pressure towards
  virus variants that escape that immune recognition pathway, e.g. through point 
  mutations that decrease binding of the respective peptide to MHC I. \\

@@

  One step in finding these mutations is through the statistical analysis
  of sequence data. However, existing methods are based on nullhypothesis significance 
  testing and do not make use of all the available information and therefore have poor
  real-world performance. \\

@@

  \textbf{Supplementary information} \\
  \url{google.de}[Supplementary data] are available at \textit{Bioinformatics} online. \\
}

@@

\section{Introduction}
\section{System and methods}
\section{Algorithm}
\section{Implementation}
\section{Discussion}
\section{References}

>>>>

\usepackage{parskip}
\usepackage{microtype}
\usepackage{svg}
\usepackage{float}
\usepackage{placeins}
\usepackage[english]{babel} % Specify a different language here - english by default
\usepackage{listings}
\usepackage{fontspec}
\usepackage{hyperref}
% \usepackage{lipsum} % Required to insert dummy text. To be removed otherwise
\setmainfont{TeX Gyre Termes}
%----------------------------------------------------------------------------------------
%	COLUMNS
%----------------------------------------------------------------------------------------

@@

\Authors{Daniel Habermann\textsuperscript{1}, Daniel Hoffmann\textsuperscript{1}} % Authors
\affiliation{\textsuperscript{1}\textit{Bioinformatics \& Computational Biophysics, Faculty of Biology, University of Duisburg-Essen, 45117 Essen, Germany}} % Author affiliation
% \affiliation{\textsuperscript{2}\textit{Department of Chemistry, University of Examples, London, United Kingdom}} % Author affiliation
% \affiliation{*\textbf{Corresponding author}: john@smith.com} % Corresponding author

@@

\Abstract{
  % - what are HLA associated mutations and why identifying HLA escape is important
  % 
  % - current methods lack important aspects
  % - Progress in Bayesian methods are not reflected in current HLA models
  % - Bayesian statistics provides a coherent framework to combine information from different sources
  % - Using this kind of imformation and new methods improve predicted performance tremendously
  % -
  \\
  \textbf{Motivation} \\
  The human leucocyte antigen system (HLA) is of paramount importance to combat viral
  infections by presenting peptides on the cell surface via MHC I.
  In this way, CD8+ cytotoxic T-Lymphocytes exert a strong selection pressure towards
  virus variants that escape that immune recognition pathway, e.g. through point 
  mutations that decrease binding of the respective peptide to MHC I. \\

@@

  One step in finding these mutations is through the statistical analysis
  of sequence data. However, existing methods are based on nullhypothesis significance 
  testing and do not make use of all the available information and therefore have
  unsatisfactory real-world performance. \\

@@

  \textbf{Supplementary information} \\
  \href{https://google.com}{Supplementary data} are available at \textit{Bioinformatics} online. \\
}

@@

\section{Introduction}

\section{System and methods}
\section{Algorithm}
\section{Implementation}
\section{Discussion}
\section{References}
